\documentclass[12pt]{article}
\usepackage{fontspec}
\usepackage{microtype}
\setmainfont[Ligatures=TeX,Numbers=Lowercase]{EB Garamond}
\pagenumbering{gobble}

\title{Animal Chess\\\textit{(Do Shou Qi)}}
\author{}
\date{}

\begin{document}
\maketitle

\begin{enumerate}
\item Each player has eight numbered animals: a \textit{rat} (1), a
\textit{cat} (2), a \textit{dog} (3), a \textit{wolf} (4), a \textit{leopard}
(5), a \textit{tiger} (6), a \textit{lion} (7), and an \textit{elephant} (8).
These animals start the game on the same-numbered square on that player's side
of the board.

\item Players take turns moving an animal. Animals can move one square forward,
backward, left, or right, but not diagonally. However, you cannot move an
animal to repeat a prior state of the game.

\item The square marked with a crown is a \textit{den}. Your animals cannot
move onto your own den, but you win if one of your animals moves onto your
opponent's den.

\item Your animals cannot move onto the same square as another of your animals,
or onto an opponent's animal with a larger number; but if one of your animals
moves onto an opponent's animal with the same or a smaller number, it is
\textit{captured} and removed from the game. As an exception, rats (1) can
capture elephants (8) instead of the reverse: this is because elephants are
afraid of rats!

\item The squares marked with $\times$'s are \textit{traps}. A trapped animal
may be captured by any kind of animal as if its number were zero. (A trapped
rat (1) may even be captured by an elephant (8).)

\item The blue squares in the middle of the board are \textit{rivers}. Animals
cannot move onto a river. As an exception, rats (1) are very good swimmers
and can move on rivers, but cannot capture when moving onto or off of a river.

\item Tigers (6) and lions (7) are very strong and can jump in a straight
line over a river in a single move: tigers (6) can jump horizontally over
two river squares, and lions (7) can jump in either direction over up to three
river squares. These animals can even capture another animal when jumping;
however, they are too afraid of the water to jump over a swimming animal.
\end{enumerate}

\end{document}
